---
title: "R Notebook"
author: "Kiki Kanik"
output: html_notebook
---
Problem I:
a.
```{r}
?read.table
```
```{r}
rain.df <- read.table("http://www.statprogr.science/data/rnf6080.dat", header = FALSE)
```
b. 
```{r}
nrow(rain.df)
ncol(rain.df)
```
c. 
```{r}
colnames(rain.df)
```
d. 
```{r}
rain.df[5,7]
```
e. 
```{r}
rain.df[2,]
```
f. 
```{r}
names(rain.df) <- c("year","month","day",seq(0,23))
```
This function created 3 columns and named them "year" "month" and “day”, and the fourth column refers to the hours in a day
g. The issue with this histogram is that we cannot have negative rain. We must fix this.
```{r}
rain.df$daily <- apply(rain.df[,c(4:27)], 1, function(x) sum(x))
hist(rain.df[,28], breaks = 25,xlab = "inches of rain", col = "lightblue", border = "blue", main = "daily rainfall")
```
h.
```{r}
rain.df.fixed <- rain.df
is.na(rain.df.fixed) <- rain.df.fixed < 0
hist(rain.df.fixed[,28], breaks = 25, xlab = "inches of rain" ,col = "lightblue", border = "blue", main = "daily rainfall")
```
Problem II:
a. i. So, since we created the vector as c("...") each of the values inside became a char String value, when perhaps they should really be Integers.
ii. finds the max value in vector1
iii. sorts the values in vector1
iv. since these values are strings, it is impossible to find the sum of Strings
```{r}
vector1 <- c("5", "12", "7", "32")
max(vector1)
sort(vector1)
sum(vector1)
```
b. i. creates vector of char Strings and integers
ii. error occurs because cannot add two char Strings together this way
iii. creates a data frame with two ints, and two chars, but allows them to keep their data types
iv. adds both ints together, this is permissible
v. creates list with two char Strings, and two ints, but allows them to keep their data types
vi. Adds the two integers together
vii. error occurs because cannot add two lists together
```{r}
vector2 <- c("5",7,12)
vector2[2] + vector2[3]
dataframe3 <- data.frame(z1="5",z2=7,z3=12)
dataframe3[1,2] + dataframe3[1,3]
list4 <- list(z1="6", z2=42, z3="49", z4=126)
list4[[2]]+list4[[4]]
list4[2]+list4[4]
```
Problem III:
a. 
```{r}
?seq
```
```{r}
seq(1, 9673, 372)
```
```{r}
seq(1, 10000, length.out=50)
```
b. off the bat, the main difference is between the verbiage times v each. after computing, i is very easy to see the differences: times will make 1 2 3 repeat 3 times, while each makes each value repeat 3 times. Although small difference in word, changes outcome totally.
```{r}
rep(1:3, times=3)
rep(1:3, each=3)
```
